\documentclass[12pt]{article}
\usepackage{lease}

\begin{document}

\begin{center}
RESIDENTIAL LEASE AGREEMENT
\end{center}

THIS LEASE (the ``Lease'') dated this $\rule{1cm}{0.15mm}$ day of
$\rule{2.5cm}{0.15mm}$, $\rule{1.5cm}{0.15mm}$

BETWEEN:\\

\begin{center}
\textbf{Beta WPI Housing Corporation}

(the ``Landlord'')

- AND-

\textbf{Brother 1, Brother 2, Brother 3, Brother 4, and Brother 5}

(collectively and individually the ``Tenant'')

(individually the ``Party'' and collectively the ``Parties'')
\end{center}

IN CONSIDERATION OF the Landlord leasing certain premises to the Tenant and
other valuable consideration, the receipt and sufficiency of which
consideration is hereby acknowledged, the Parties agree as follows:

\section*{Leased Property}

\begin{enumerate}

    \item The Landlord agrees to rent to the Tenant the house, municipally
	    described as 52 Fruit St \#X, Worcester, MA 01609 (the ``Property''),
		for use as residential premises only.  
    \item Subject to the provisions of this Lease, apart from the Tenant, no
	    other persons will live in the Property without the prior written
		permission of the Landlord.
    \item No guests of the Tenants may occupy the Property for longer than one
	    week without the prior written consent of the Landlord.
    \item No animals are allowed to be kept in or about the Property.
    \item Subject to the provisions of this Lease, the Tenant is entitled to
	    the exclusive use of the following parking on or about the
		Property: Driveway.
    \item The Tenant and members of Tenant's household will not smoke inside
	    the Property nor permit any guests or visitors to smoke in the
		Property.
    \item The Tenant and members of Tenant's household will not vape inside the
	    Property nor permit any guests or visitors to vape in the Property.

\end{enumerate}
    
    
\section*{Term}

\begin{enumerate}[resume]
    \item The term of the Lease is a periodic tenancy commencing at 12:00 noon
	    on July 1, 2021 and continuing on a year-to-year basis until the
		Landlord or the Tenant terminates the tenancy.
   \item  Any notice to terminate this tenancy must comply with the applicable
	   legislation of the Commonwealth of Massachusetts (the ``Act'').
\end{enumerate}
   
\section*{Rent}

\begin{enumerate}[resume]
    \item Subject to the provisions of this Lease, the rent for the Property is
	    \$XXX.00 per month (the ``Rent'').
    \item The Tenant will pay the Rent on a semianual basis, once on or before
        the first (1st) day of the lease term, and once on or before the first
        day of seventh (7th) month of the lease term, to the Landlord via
		Billhighway.
    \item The Landlord may increase the Rent for the Property upon providing to
	    the Tenant such notice as required by the Act.
    \item The Tenant will be charged an additional amount of \$15.00 per day
	    for any Rent that is received after the greater of 30 days after
		the due date and any mandatory grace period required under the
		Act, if any.
\end{enumerate}
    
\section*{Inspections}

\begin{enumerate}[resume]
    \item The Parties will complete, sign and date an inspection report at the
	    beginning and at the end of this tenancy.
    \item At all reasonable times during the term of this Lease and any renewal
	    of this Lease, the Landlord and its agents may enter the Property
		to make inspections or repairs, or to show the Property to
		prospective tenants or purchasers in compliance with the Act.
\end{enumerate}
    
\section*{Tenant Improvements}

\begin{enumerate}[resume]
    \item The Tenant may NOT make improvements to the Property.
\end{enumerate}    
   
\section*{Utilities and Other Charges}

\begin{enumerate}[resume]
    \item The Landlord is responsible for the payment of the following
	    utilities and other charges in relation to the Property:
		electricity, water/sewer, internet, natural gas and heating
		oil/propane.
\end{enumerate}
   
\section*{Insurance}

\begin{enumerate}[resume]  
    \item The Tenant is hereby advised and understands that the personal
	    property of the Tenant is not insured by the Landlord for either
		damage or loss, and the Landlord assumes no liability for any
		such loss.
    \item The Tenant is not responsible for insuring the Landlord's contents
	    and furnishings in or about the Property for either damage or loss,
		and the Tenant assumes no liability for any such loss.
\end{enumerate}
    
\section*{Attorney Fees}
\begin{enumerate}[resume]
    \item In the event that any action is filed in relation to this Lease, the
	    unsuccessful Party in the action will pay to the successful Party,
		in addition to all the sums that either Party may be called on
		to pay, a reasonable sum for the successful Party's attorney
		fees.
\end{enumerate}
   
\section*{Governing Law}
\begin{enumerate}[resume]
    \item This Lease will be construed in accordance with and exclusively
	    governed by the laws of the Commonwealth of Massachusetts.
\end{enumerate}
    
\section*{Severability}
\begin{enumerate}[resume]
    \item If there is a conflict between any provision of this Lease and the
	    Act, the Act will prevail and such provisions of the Lease will be
		amended or deleted as necessary in order to comply with the
		Act. Further, any provisions that are required by the Act are
		incorporated into this Lease.
    \item The invalidity or unenforceability of any provisions of this Lease
	    will not affect the validity or enforceability of any other
		provision of this Lease.  Such other provisions remain in full
		force and effect.
\end{enumerate}
    
\section*{Amendment of Lease}
\begin{enumerate}[resume]
   \item  This Lease may only be amended or modified by a written document
	   executed by the Parties.
\end{enumerate}    
    
\section*{Assignment and Subletting}
\begin{enumerate}[resume]
    \item The Tenant will not assign this Lease, or sublet or grant any
	    concession or license to use the Property or any part of the
		Property. Any assignment, subletting, concession, or license,
		whether by operation of law or otherwise, will be void and
		will, at Landlord's option, terminate this Lease.
\end{enumerate}
    
\section*{Additional Clause}
\begin{enumerate}[resume]
    \item The Tenant shall not wear shoes while indoors. If needed, shoe
	    storage will be provided in the front porch area.
\end{enumerate}
    
\section*{Damage to Property}
\begin{enumerate}[resume]
    \item If the Property should be damaged other than by the Tenant's
	    negligence or willful act or that of the Tenant's employee, family,
		agent, or visitor and the Landlord decides not to rebuild or
		repair the Property, the Landlord may end this Lease by giving
		appropriate notice.
\end{enumerate}
    
\section*{Care and Use of Property}
\begin{enumerate}[resume]
    \item The Tenant will promptly notify the Landlord of any damage, or of any
	    situation that may significantly interfere with the normal use of
		the Property or to any furnishings supplied by the Landlord.
    \item The Tenant will not engage in any illegal trade or activity on or
	    about the Property.
    \item The Parties will comply with standards of health, sanitation, fire,
	    housing and safety as required by law.
    \item The Parties will use reasonable efforts to maintain the Property in
	    such a condition as to prevent the accumulation of moisture and the
		growth of mold. The Tenant will promptly notify the Landlord in
		writing of any moisture accumulation that occurs or of any
		visible evidence of mold discovered by the Tenant. The Landlord
		will promptly respond to any such written notices from the
		Tenant.
    \item If the Tenant is absent from the Property and the Property is
	    unoccupied for a period of 4 consecutive days or longer, the Tenant
		will arrange for regular inspection by a competent person. The
		Landlord will be notified in advance as to the name, address
		and phone number of the person doing the inspections.
    \item At the expiration of the term of this Lease, the Tenant will quit and
	    surrender the Property in as good a state and condition as they
		were at the commencement of this Lease, reasonable use and wear
		and tear excepted.
\end{enumerate}
    
\section*{Rules and Regulations}
\begin{enumerate}[resume]
    \item The Tenant will obey all rules and regulations of the Landlord
	    regarding the Property.
\end{enumerate}
    
\section*{Address for Notice}
\begin{enumerate}[resume]
    \item For any matter relating to this tenancy, the Tenant may be contacted
	    at the Property or through the phone number below:
	Name: Brother 1, Brother 2, Brother 3 and Brother 4.
	Phone: \rule{3cm}{0.15mm}.
    \item For any matter relating to this tenancy, whether during or after this tenancy has been terminated, the Landlord's address for notice is:\\
        Name: Beta WPI Housing Corporation.\\
        Address: 52 Fruit St, Worcester MA, 01609.\\\\
        The contact information for the Landlord is:\\
        Phone:  (571) 230-6476.\\
        Email: betawpihc@gmail.com
\end{enumerate}
        
\section*{General Provisions}
\begin{enumerate}[resume]
    \item All monetary amounts stated or referred to in this Lease are based in
	    the United States dollar.
    \item Any waiver by the Landlord of any failure by the Tenant to perform or
	    observe the provisions of this Lease will not operate as a waiver
		of the Landlord's rights under this Lease in respect of any
		subsequent defaults, breaches or non-performance and will not
		defeat or affect in any way the Landlord's rights in respect of
		any subsequent default or breach.
    \item This Lease will extend to and be binding upon and inure to the
	    benefit of the respective heirs, executors, administrators,
		successors and assigns, as the case may be, of each Party. All
		covenants are to be construed as conditions of this Lease.
    \item All sums payable by the Tenant to the Landlord pursuant to any
	    provision of this Lease will be deemed to be additional rent and
		will be recovered by the Landlord as rental arrears.
    \item Where there is more than one Tenant executing this Lease, all Tenants
	    are jointly and severally liable for each other's acts, omissions
		and liabilities pursuant to this Lease.
    \item Locks may not be added or changed without the prior written agreement
	    of both Parties, or unless the changes are made in compliance with
		the Act.
    \item The Tenant will be charged an additional amount of \$0.00 for each
	    N.S.F. check or checks returned by the Tenant's financial
		institution.
    \item Headings are inserted for the convenience of the Parties only and are
	    not to be considered when interpreting this Lease. Words in the
		singular mean and include the plural and vice versa. Words in
		the masculine mean and include the feminine and vice versa.
    \item This Lease may be executed in counterparts. Facsimile signatures are
	    binding and are considered to be original signatures.
    \item This Lease constitutes the entire agreement between the Parties.
    \item Time is of the essence in this Lease.
\end{enumerate}

\clearpage

IN WITNESS WHEREOF Brother 1, Brother 2, Brother 3 and Brother 4 and Beta WPI
Housing Corporation have duly affixed their signatures on $\rule{1cm}{0.15mm}$
day of $\rule{2.5cm}{0.15mm}$, $\rule{1.5cm}{0.15mm}$.
  	

\begin{flushright} Beta WPI Housing Corporation

\vspace{1cm}

Per: $\rule{7cm}{0.15mm}$ (Seal)
  	

\signature{Brother 1}

\signature{Brother 2}

\signature{Brother 3}

\signature{Brother 4}

\signature{Brother 5} \end{flushright}

\clearpage

The Tenant acknowledges receiving a duplicate copy of this Lease signed by the
Tenant and the Landlord on the $\rule{1cm}{0.15mm}$ day of
$\rule{2.5cm}{0.15mm}$, 20$\rule{1cm}{0.15mm}$.
  	
\begin{flushright}

\signature{Brother 1}

\signature{Brother 2}

\signature{Brother 3}

\signature{Brother 4}

\signature{Brother 5}

\end{flushright}

\clearpage
\guaranty{}
\clearpage
\guaranty{}
\clearpage
\guaranty{}
\clearpage
\guaranty{}
\clearpage
\guaranty{}
\clearpage

\end{document}
